### 2020-05-11 README.Rmd
Cleaned up makehtml and extended running_aMSE.Rmd. No Errors, Warnings, or Notes
Higher level functions, such as setupregion now simplify the running. No Errors, Warnings, or Notes

```{r example}
# basic example code
library(aMSE)
library(rutilsMH)

  data(region1)
  glb <- region1$globals
  data(testregC)
  data(testregD)
  regDe <- testequil(regC=testregC,regD=testregD,glob=glb)
  str(regDe)

@@

### 29/04/2020

Now developing a vignette entitled _Running_aMSE_, which contains some worked examples to get a user moving in the uise of __aMSE__. There remains much development still to do.

>>>>

```{r example}
# a minimal example
starttime <- as.character(Sys.time())
library(aMSE)
# Obviously you should modify the rundir to suit your own computer
rundir <- "./../../rcode2/aMSEUse/run2"
outdir <- setupdirs(rundir)
datadir <- outdir$datadir # this usually has the data files 
resdir <- outdir$resdir   # this holds all results

data(ctrl)
data(constants)
data(region1)
glb <- region1$globals
runname <- ctrl$runlabel

out <- setupregion(constants, glb, region1)
regionC <- out$regionC
regionD <- out$regionD
product <- out$product  # important bits usually saved in resdir
# did the larval dispersal level disturb the equilibrium?
regDe <- testequil(regionC,regionD,glb)

resfile <- setuphtml(resdir,runname)  # prepare to log results
plotproductivity(resdir,runname,product,glb)
biology_plots(resdir, runname, glb, regionC, regionD, product)
numbersatsize(resdir, runname, glb, regionD)

endtime <- as.character(Sys.time())

reportlist <- list(runname=runname,
  starttime=starttime,endtime=endtime,
  regionC=regionC,
  regionD=regionD,
  product=product,
  glb=glb,constants=constants
)

runnotes <- "This is a bare-bones example."
# If you unhash this last function call it will generate and open a 
# local website inside resdir so you can see the results so far.

# make_html(replist=reportlist,rundir=rundir,width=500,
#           openfile=TRUE,runnotes=runnotes,verbose=FALSE)

@@

See the vignette Running_aMSE.Rmd for a more detailed example.

See the New.Rd for recent developments
